\documentclass{sig-alternate}

\begin{document}
	\title{CSCI-620 Data Mining with the Airbnb Dataset}
	\subtitle{[Exploring and Mining the dataset of NY Airbnbs]}
	
	\numberofauthors{4}
	\author
	{
		\alignauthor
		Aishwarya Rao
		\email{ar2711@rit.edu}
		\alignauthor
		Apurav Khare
		\email{ak2816@rit.edu}
		\and
		\alignauthor
		Martin Qian
		\email{jq3513@rit.edu}
		\alignauthor
		Prateek Kalasannavar
		\email{pk6685@rit.edu}
	}
	
	\maketitle
	\begin{abstract}
		
	
	\end{abstract}
	
	\section{Trials on the dataset}
	\subsection{Decision Tree}
	Decision Tree is a algorithm about

	Because the data has many attributes of discrete, in order to do decision tree on our dataset, 
	At first we did some simple modifications to the data. These modifications will be applied to 
	the other 2 algorithms, too. What we did first was to remove all the extreme data, such as the data with prices
	that are 0 meaning these hosts are totally free or that are too expensive that are higher than 1000 dollars. These
	data is generated in abnormal conditions and will greatly impact the result of decision tree model.
	Secondly, we kept all the attributes of numberics and discarded other attributes. This step might looks like controversial
	yet as we are doing just test, we think it is okay. Moreover, our aim is to make predictions yet decision tree
	can only do classification, so we converted the aim attribute price from numberics to boolean value. 
	In the end, we divided dataset to train and test by 9:1. 

	The final result is about 72\% and concrete report can be found here

	\subsection{k nearest neighbours}
	k nearest neighbours(kNN) is about

	the data processed by kNN needs to be normalized because it used distance to show varieties. 
	What's more, k of kNN is a hyper-parameter, and a popular choice of k is between 5-20.

	after doing the same process, the final result of kNN is 64\% with k=20. Report

	\subsection{Naive Bayes}
	Naive Bayes is about
	Naive Bayes is good resistance to noise compared to the former 2. 
	
	the result of Naive Bayes is 68\%. Report

	\subsection{summaries}


	\section{Future plan}
	
\end{document}